Rapid Cycleway Prioritisation Tool

### 2020-06-09 code/index.Rmd
Close #70

```{r}
pvars = c("Name", "Level")
tm_shape(regions) + tm_polygons("Level", popup.vars = pvars) 
  # + tm_shape(regions_centroids) + tm_text("Name", size = 0.7)
```

>>>>

```{r}
# pvars = c("Name", "Level")
# tm_shape(regions) + tm_polygons("Level", popup.vars = pvars) 
  # + tm_shape(regions_centroids) + tm_text("Name", size = 0.7)
library(leaflet)
leaflet(data = (regions)) %>% 
  addTiles(urlTemplate = "//b.tile-cyclosm.openstreetmap.fr/cyclosm/{z}/{x}/{y}.png") %>% 
  addPolygons(popup = ~url, fillOpacity = 0, weight = 1) 
  # addLabelOnlyMarkers(data = regions_centroids, label = ~as.character(Name), 
  #                     labelOptions = labelOptions(noHide = T, direction = 'top', textOnly = T)
  #                     )
```
